%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Large \scshape Jonathan Botros} \\ \vspace{1pt}
    \small  \href{mailto:jbotros7@gmail.com}{\underline{jbotros7@gmail.com}} $|$ 
    \href{https://linkedin.com/in/joneb}{\underline{linkedin.com/in/joneb}} $|$
    \href{https://github.com/jonebdev}{\underline{github.com/jonebdev}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {New Jersey Institute of Technology}{Newark, NJ}
      {Bachelor of Arts in Computer Science}
      {September 2016 -- May 2020}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    % \resumeSubheading
    %   {Undergraduate Research Assistant}{June 2020 -- Present}
    %   {Texas A\&M University}{College Station, TX}
    %   \resumeItemListStart
    %     \resumeItem{Developed a REST API using FastAPI and PostgreSQL to store data from learning management systems}
    %     \resumeItem{Developed a full-stack web application using Flask, React, PostgreSQL and Docker to analyze GitHub data}
    %     \resumeItem{Explored ways to visualize GitHub collaboration in a classroom setting}
    %   \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Lead Software Engineer}{April. 2023 -- Present}
      {Kenvue (Formerly Known as Johnson \& Johnson Consumer Health)}{Skillman, NJ}
      \resumeItemListStart
        \resumeItem{Lead Platform Engineer for Kenvue's Software Engineering Portal, built with Typescript, React and Express.js, that improved developer productivity by allowing engineers to catalog  projects, integrate with DevOps tooling, and allows developers to quickly stand up new projects with CI/CD pipelines through a simple form. }
        \resumeItem{Enabling Software Engineering standards across the across the organization, giving guidance and standards for enabling adoption for lightweight, containerized microservices. Containerized lubriderm.com, motrin.com and several other high profile sites deployed them on to a shared Kubernetes cluster. }
    \resumeItemListEnd

    \resumeSubheading
      {Senior Software Developer}{May 2022 -- March 2023}
      {Johnson \& Johnson}{Raritan, NJ}
      \resumeItemListStart
        \resumeItem{Developed an internal mobile application for labeling images built in React Native where the data generated trained 10+ supervised machine learning models to be used in Ethicon Products.}
        \resumeItem{Established CI/CD Jenkins pipeline for the app portal which ran unit tests, lints backend code, runs static analysis via
Sonarqube, and deploys to the various EC2 environments which resulted in increased developer efficiency.}
        \resumeItem{Rearchitected frontend web portal with React.js solution built with Vite, Tailwind and Typescript for the data science
team to visualize data captured from the app and carry out administrative tasks more effectively.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Developer}{June 2020 -- May 2022}
      {Johnson \& Johnson}{Raritan, NJ}
      \resumeItemListStart
        \resumeItem{ Lead Backend PHP Developer for Care4Today, a mobile app that connected patients to their doctor to keep track of
their symptoms, medication adherence and appointments. New trackers were developed so that those metrics could be aggregated to generate a Risk Score, which resulted in 100 {plus} new sites onboarded for clinical studies.}
        \resumeItem{ Developed serverless Node.js REST API for an internal mobile app to retrieve hashed codes stored in a PostgreSQL database for the Janssen Covid Vaccine.}
        \resumeItem{ Backend Node.JS API Developer for the Johnson and Johnson API Catalog,  which hosts over 150 APIs across Johnson \& Johnson for internal discovery. Developed CI/CD tools to enable teams to upload their OpenAPI docs to the API Catalog}

      \resumeItemListEnd
        \resumeSubheading
      {Software Engineering Co-op}{June 2020 -- May 2022}
      {Johnson \& Johnson}{Raritan, NJ}
      \resumeItemListStart
        \resumeItem{ Migrated 10+ APIs from the Apigee Trireme hosting
service to Apigee’s Hosted Targets server solution, and provided support for 4 overseas teams to migrate their APIs for a critical API Migration project.}
        \resumeItem{ Full Stack Developer for an internal developer companion application, developed with Node.js \& React. The system provided a centralized source of data pooled from developer applications, including
Bitbucket, SonarQube, and Jenkins, resulting in valuable metrics for over 100 active Johnson \& Johnson projects.}

      \resumeItemListEnd
  \resumeSubHeadingListEnd



%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart

        \resumeProjectHeading
          {\textbf{Spotify to Apple Music Playlist Converter} $|$ \emph{React, Node.js}}
          {}
          \resumeItemListStart
            \resumeItem{ REST API \& Frontend website that can take a playlist from Apple Music or Spotify and be able to migrate that playlist to the other respective service. Integrated with both the Apple Music and Spotify REST APIs}
          \resumeItemListEnd
        \resumeProjectHeading
          {\textbf{Color Fun Run} $|$ \emph{PHP, HTML, Javascript, MySQL}}{}
          \resumeItemListStart
            \resumeItem{ Registration form for an charity event that integrated with the Paypal SDK that allowed users to register and pay for color run. User info was stored in a database and the event team was notified when a person registered. The event had 180+ attendees and raised \$12,000 to build wells for the needy in Africa.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Javascript, Typescript, Python, PHP, Bash, Java, HTML, CSS, Groovy} \\
     \textbf{Frameworks}{: React, Node.js, Flask, JUnit, WordPress, Material-UI, FastAPI} \\
     \textbf{Developer Tools}{: Git, Docker, Kubernetes, Jenkins, AWS, Apigee, VSCode, Jenkins, Jira, ArgoCD} \\
     \textbf{Libraries}{: pandas, NumPy, Matplotlib}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
